### 2021-12-06 lmcs/introduction.tex
polishing

\begin{quotation}
  \textbf{RQ:}
  Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?
\end{quotation}

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18extended} and PGV.
We make the following main contributions:
\begin{enumerate}[labelindent=0pt,labelwidth=1.333\parindent,align=left,labelsep*=0pt,leftmargin=!]
\item[(\cref{sec:pgv})] \textbf{Priority GV}. We present Priority GV (\cref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove \emph{subject reduction} (\cref{thm:pgv-subject-reduction-confs}) and \emph{progress} (\cref{thm:pgv-closed-progress-confs}). We addresses several problems in the original GV language, most notably:
  \begin{enumerate}
  \item PGV does not require the pseudo-type $S^\sharp$; and
  \item its structural congruence is type preserving.
  \end{enumerate}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item[(\cref{sec:pcp})] \textbf{Translation from PCP to PGV}.
  We present a \emph{sound and complete encoding} of PCP~\cite{dardhagay18extended} in PGV (\cref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).
  To obtain a tight correspondence, we update PCP, moving away from commuting conversions and reduction as cut elimination towards reduction based on structural congruence, as it is standard in process calculi.
\end{enumerate}

>>>>

\vspace{1em}
  \textbf{RQ:}
  \emph{Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?}
\vspace{1em}

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18extended} and PGV.

We make the following main contributions:
\begin{enumerate}
\item \textbf{Priority GV}. We present Priority GV (\cref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove \emph{subject reduction} (\cref{thm:pgv-subject-reduction-confs}) and \emph{progress} (\cref{thm:pgv-closed-progress-confs}).

We addresses several problems in the original GV language, most notably:
  \begin{enumerate}
  \item PGV does not require the pseudo-type $S^\sharp$;
  \item Structural congruence is type preserving.
  \end{enumerate}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item \textbf{Translation from PCP to PGV}.
  We present a \emph{sound and complete encoding} of PCP~\cite{dardhagay18extended} in PGV (\cref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).

  To obtain a tight correspondence, we update PCP, moving away from commuting conversions and reduction as cut elimination towards reduction based on structural congruence, as it is standard in process calculi.
\end{enumerate}
